---
title: "SOCS0100_report"
format: html
editor: visual
---

## Part I-A Data Exploration and Contextualisation

### Introduction (Structure, variable and contextual relevance of the dataset

I choose to analyse the [share of the population with access to electricity and clean fuels for cooking](https://github.com/owid/owid-datasets/blob/master/datasets/Number%20of%20people%20with%20and%20without%20energy%20access%20(OWID%20based%20on%20World%20Bank%2C%202021)/Number%20of%20people%20with%20and%20without%20energy%20access%20(OWID%20based%20on%20World%20Bank%2C%202021).csv) dataset (World Bank, 2021).

First, I ran the

### Overview of the dataset

## Part I-B Data Processing and Functional Programming

## Part II-A Data Visualisation and Functional Programming

## Part II-B Reproducibility

## Part II-C Critical engagement with AI: ChatGPT

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
